---
title: "Deployment Practice"
format: html
editor: visual
---

## Intro

This is practice for Github pages deployments. The goal is to create a working web page, break the deployment through pushing commits, and subsequently fix it without deleting the repo.

## Working version

### Original push
This is some text. Below is code that works.

This is a good stopping point. I'll add and commit this. 

```{r}
plot(faithful)
```

## Update to web page

This section is added after the first working deployment. I'll save this, render again, add everything, and commit. I expect the deployment to stop working once I do this.

```{r}
plot(mtcars$wt, mtcars$mpg)
```

## Another addition

So the previous added section didn't break anything, which was a pleasant surprise. This means that adding content to our Quarto file then rendering the new output, adding and then pushing to remote shouldn't break anything. 

Final add. If it breaks deployment, next update will be hopefully restoring a working deployment.

```{r}
mpg_mod <- lm(mpg ~ wt, data = mtcars)

par(mfrow = c(2, 2))
plot(mpg_mod)
par(mfrow = c(1,1))
```

